---
title: "Chronic infections reduce mortality following unrelated secondary infections in Drosophila melanogaster"
author: "Abigail Wukitch"
date: "11/10/2021"
editor_options:
  chunk_output_type: console
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    theme: cerulean
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ready the workspace
Load all necessary libraries, packages, and data files
```{r, load libraries and data}
library(survival)
library(RColorBrewer)
library(ggplot2)
library(rlang)
library(agricolae)

rm(list=ls()) #removes all old variables
E.fae_P.rett = read.csv("E.fae-P.rett.csv")
E.fae_bacterial_load = read.csv("E.fae bacterial load data.csv")
S.m_P.rett_no_extremes = read.csv("S.m-P.rett no extremes.csv")
S.m_bacterial_load = read.csv("S.m bacterial load data.csv")
S.m_P.rett_extremes = read.csv("S.m-P.rett extremes.csv")
S.m_P.snee = read.csv("S.m-P.snee.csv")
P.rett_varied_primary = read.csv("Varied primary S.m-P.rett.csv")
P.snee_varied_primary = read.csv("Varied primary S.m-P.snee.csv")

#S.m_P.rett_no_extremes 7/10/18 is the problematic one - need to delete
#S.m_P.rett_no8 <- subset(S.m_P.rett_no_extremes, date == "6/14/2019" | date == "6/17/2019" | date == "6/19/2019" | date == "6/25/2019" | date == "6/27/2019" | date == "6/28/2019" | date == "8/2/2018" | date == "8/6/2018")
#table(S.m_P.rett_no8$date, S.m_P.rett_no8$secondary_dose)

#write.csv(S.m_P.rett_no8, "S.m_P.rett no extremes.csv")
```
## Figure 1A {.tabset}
Chronic infections with S. marcescens provided protection against mortality following secondary infection with P. rettgeri

### Graph
Mortality following secondary infection with P. rettgeri in flies chronically infected with S. marcescens versus control flies not given a chronic infection. Flies chronically infected with S. marcescens were more likely to survive various doses of secondary infection with P. rettgeri (p < 0.0001).

```{r, S.m-P.rett no extremes survival data}
S.m_P.rett_no_extremes$primary <- ordered(S.m_P.rett_no_extremes$primary, levels = c("PBS", "S.m"))
#table(S.m_P.rett_no_extremes$primary, S.m_P.rett_no_extremes$secondary_dose)

S.m_bacterial_load$primary <- ordered(S.m_bacterial_load$primary, levels = c("PBS", "S.m"))
#table(S.m_bacterial_load$primary, S.m_bacterial_load$secondary_dose)

#THE GRAPH
#png(file="S.m_P.rett_no_extremes.png",width=1200,height=900,res=130)
par(mar=c(4,5,1,1)) #sets the margins around the graph so there is room for the labels
plot(survfit(Surv(S.m_P.rett_no_extremes$day, S.m_P.rett_no_extremes$status) ~ S.m_P.rett_no_extremes$primary + S.m_P.rett_no_extremes$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Statistics
```{r}
#STATISTICS
S.m_P.rett_no_extremes$secondary_dose <- as.factor(S.m_P.rett_no_extremes$secondary_dose)
S.m_P.rett_no_extremes_coxph <- coxph(Surv(day, status) ~ secondary_dose + primary + rep + primary:secondary_dose + rep:secondary_dose + rep:primary, data = S.m_P.rett_no_extremes)
#summary(S.m_P.rett_no_extremes_coxph)
anova(S.m_P.rett_no_extremes_coxph)
```

### Block 1
```{r}
S.m_P.rett_no_extremes_block1 <- subset(S.m_P.rett_no_extremes, date == "8/2/2018")
table(S.m_P.rett_no_extremes_block1$primary, S.m_P.rett_no_extremes_block1$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block1$day, S.m_P.rett_no_extremes_block1$status) ~ S.m_P.rett_no_extremes_block1$primary + S.m_P.rett_no_extremes_block1$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5"), lty=c(3, 3, 3, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5"),lty=c(3, 3, 3, 1, 1, 1),lwd=5, cex=1)
```

### Block 2
```{r}
S.m_P.rett_no_extremes_block2 <- subset(S.m_P.rett_no_extremes, date == "8/6/2018")
table(S.m_P.rett_no_extremes_block2$primary, S.m_P.rett_no_extremes_block2$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block2$day, S.m_P.rett_no_extremes_block2$status) ~ S.m_P.rett_no_extremes_block2$primary + S.m_P.rett_no_extremes_block2$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5"), lty=c(3, 3, 3, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5"),lty=c(3, 3, 3, 1, 1, 1),lwd=5, cex=1)
```

### Block 3
```{r}
S.m_P.rett_no_extremes_block3 <- subset(S.m_P.rett_no_extremes, date == "6/14/2019")
table(S.m_P.rett_no_extremes_block3$primary, S.m_P.rett_no_extremes_block3$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block3$day, S.m_P.rett_no_extremes_block3$status) ~ S.m_P.rett_no_extremes_block3$primary + S.m_P.rett_no_extremes_block3$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```


### Block 4
```{r}
S.m_P.rett_no_extremes_block4 <- subset(S.m_P.rett_no_extremes, date == "6/17/2019")
table(S.m_P.rett_no_extremes_block4$primary, S.m_P.rett_no_extremes_block4$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block4$day, S.m_P.rett_no_extremes_block4$status) ~ S.m_P.rett_no_extremes_block4$primary + S.m_P.rett_no_extremes_block4$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 5
```{r}
S.m_P.rett_no_extremes_block5 <- subset(S.m_P.rett_no_extremes, date == "6/19/2019")
table(S.m_P.rett_no_extremes_block5$primary, S.m_P.rett_no_extremes_block5$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block5$day, S.m_P.rett_no_extremes_block5$status) ~ S.m_P.rett_no_extremes_block5$primary + S.m_P.rett_no_extremes_block5$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 6
```{r}
S.m_P.rett_no_extremes_block6 <- subset(S.m_P.rett_no_extremes, date == "6/25/2019")
table(S.m_P.rett_no_extremes_block6$primary, S.m_P.rett_no_extremes_block6$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block6$day, S.m_P.rett_no_extremes_block6$status) ~ S.m_P.rett_no_extremes_block6$primary + S.m_P.rett_no_extremes_block6$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 7
```{r}
S.m_P.rett_no_extremes_block7 <- subset(S.m_P.rett_no_extremes, date == "6/27/2019")
table(S.m_P.rett_no_extremes_block7$primary, S.m_P.rett_no_extremes_block7$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_no_extremes_block7$day, S.m_P.rett_no_extremes_block7$status) ~ S.m_P.rett_no_extremes_block7$primary + S.m_P.rett_no_extremes_block7$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "S.m-P.rett 0.01", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

## Figure 1B {.tabset}
Chronic infections with E. faecalis provided protection against mortality following secondary infection with P. rettgeri 

### Graph
Mortality following secondary infection with P. rettgeri in flies chronically infected with S. marcescens versus control flies not given a chronic infection. Flies chronically infected with S. marcescens were more likely to survive various doses of secondary infection with P. rettgeri (p < 0.0001).

```{r, E.fae-P.rett survival data}
E.fae_P.rett$primary <- ordered(E.fae_P.rett$primary, levels = c("PBS", "E.fae"))

E.fae_bacterial_load$primary <- ordered(E.fae_bacterial_load$primary, levels = c("PBS", "E.fae"))

#KAPLAN MEIER
#table(E.fae_P.rett$primary, E.fae_P.rett$secondary_dose) #tells you the number of flies in each condition
#png(file="E.fae-P.rett.png", width=1200, heigh=900, res=130) #determines where the graph will be saved
par(mar=c(4,5,1,1)) #sets the margins around the graph so there is room for the labels
#The graph
plot(survfit(Surv(E.fae_P.rett$day, E.fae_P.rett$status) ~ E.fae_P.rett$primary + E.fae_P.rett$secondary_dose), 
     col=c("#B5E8FC", "#09B6FC", "#055df5", "#0600a8"), #line color, cycles through
     lty=c(3, 3, 3, 3, 1, 1, 1, 1), #line type
     lwd=5, #line width
     yaxt='n', #hide the y axis so I can customize it
     xaxt='n', #hide the x axis so I can customize itS
     ylab="proportion alive", #label for the y-axis
     xlab="days post-secondary infection", #label for the x-axis
     cex.lab=2.5, #font size of axis labels
     xlim=c(0,7), #determines range of the x-axis
     xaxs='i') #makes the data flush with the axis 
#Y axis
axis(2, #left side
     las=2, #perpendicular to the axis
     cex.axis=1.5, #font size
     lwd=5) #line width
#X axis
axis(1, #bottom of the graph
     cex.axis=1.5, #font size
     lwd=5) #line width
box(lwd=5)
#The legend
legend("topright", #location
       bty="n", #no box around the legend
       c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"), #labels in the legend
       col=c("#B5E8FC", "#09B6FC", "#055df5", "#0600a8"), #colors for the legend lines, cycles through
       lty=c(3, 3, 3, 3, 1, 1, 1, 1), #line type for legend lines
       lwd=5, #line width for legend lines
       cex=1) #font size
```

### Statistics
```{r}
#SURVIVAL STATISTICS
#Generate a Cox proportional Hazards model which assesses the contribution of infectious dose while controlling for replicate
E.fae_P.rett$secondary_dose <- as.factor(E.fae_P.rett$secondary_dose)
E.fae_P.rett_coxph <- coxph(Surv(day, status) ~ secondary_dose + primary + rep + primary:secondary_dose + rep:secondary_dose + rep:primary, data = E.fae_P.rett)
#summary(E.fae_P.rett_coxph)
anova(E.fae_P.rett_coxph)

table(E.fae_P.rett$rep, E.fae_P.rett$secondary_dose)

```

### Block 1
```{r}
E.fae_P.rett_block1 <- subset(E.fae_P.rett, Date == "6/11/2019")
par(mar=c(4,5,1,1))
plot(survfit(Surv(E.fae_P.rett_block1$day, E.fae_P.rett_block1$status) ~ E.fae_P.rett_block1$primary + E.fae_P.rett_block1$secondary_dose), col=c("#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 1, 1, 1),lwd=5, cex=1)
```

### Block 2
```{r}
E.fae_P.rett_block2 <- subset(E.fae_P.rett, Date == "6/22/2018")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block2$day, E.fae_P.rett_block2$status) ~ E.fae_P.rett_block2$primary + E.fae_P.rett_block2$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 3
```{r}
E.fae_P.rett_block3 <- subset(E.fae_P.rett, Date == "6/25/2018")
par(mar=c(4,5,1,1))
plot(survfit(Surv(E.fae_P.rett_block3$day, E.fae_P.rett_block3$status) ~ E.fae_P.rett_block3$primary + E.fae_P.rett_block3$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 4
```{r}
E.fae_P.rett_block4 <- subset(E.fae_P.rett, Date == "6/3/2019")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block4$day, E.fae_P.rett_block4$status) ~ E.fae_P.rett_block4$primary + E.fae_P.rett_block4$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 5
```{r}
E.fae_P.rett_block5 <- subset(E.fae_P.rett, Date == "6/5/2019")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block5$day, E.fae_P.rett_block5$status) ~ E.fae_P.rett_block5$primary + E.fae_P.rett_block5$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 6
```{r}
E.fae_P.rett_block6 <- subset(E.fae_P.rett, Date == "7/1/2019")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block6$day, E.fae_P.rett_block6$status) ~ E.fae_P.rett_block6$primary + E.fae_P.rett_block6$secondary_dose), col=c("#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3,  1, 1, 1),lwd=5, cex=1)
```

### Block 7
Not sure why the data stops after 3 days, Frank did this one
```{r}
E.fae_P.rett_block7 <- subset(E.fae_P.rett, Date == "7/19/2018")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block7$day, E.fae_P.rett_block7$status) ~ E.fae_P.rett_block7$primary + E.fae_P.rett_block7$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 8
something seems very wrong with this
there are only 7 flies for chronically infected with the highest dose and 9 for the second highest
I did this one but need to check my binder to see why I did it like this
```{r}
E.fae_P.rett_block8 <- subset(E.fae_P.rett, Date == "7/3/2019")
par(mar=c(4,5,1,1)) 
plot(survfit(Surv(E.fae_P.rett_block8$day, E.fae_P.rett_block8$status) ~ E.fae_P.rett_block8$primary + E.fae_P.rett_block8$secondary_dose), col=c("#B5E8FC",  "#09B6FC", "#055df5", "#003694"), lty=c(3, 3, 3, 3, 1, 1, 1, 1), lwd=5,yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i')  
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)
legend("topright",inset=0, bty="n" , c("PBS-P.rett 0.001", "PBS-P.rett 0.01", "PBS-P.rett 0.1", 'PBS-P.rett 1.0', "E.fae-P.rett 0.001", "E.fae-P.rett 0.01", "E.fae-P.rett 0.1", "E.fae-P.rett 1.0"),col=c("#B5E8FC", "#09B6FC", "#055df5", "#003694"),lty=c(3, 3, 3, 3, 1, 1, 1, 1),lwd=5, cex=1)
```



## Figure 2A {.tabset}

### Graph
The calculated bacterial load after secondary infection with P. rettgeri for flies chronically infected with S. marcescens (n = 505) versus control flies (n = 506). Chronic infection with S. marcescens resulted in lowered calculated bacterial load post secondary infection. 
```{r}
#png(file="S.m_P.rett_bacterial_load.png", width=1200, height=900, res=130)
ggplot(S.m_bacterial_load, aes(x = as.character(secondary_dose), y = log(load_10hr), fill = primary)) +
  scale_fill_manual(values=c("gray", "#09b6fc")) +
  geom_boxplot() + 
  theme_classic(base_size = 25) + 
  xlab("secondary dose of P. rettgeri") +
  ylab("log(calculated bacterial load)") +
  geom_point(color = "black", size = 1.1, position=position_jitterdodge())
#dev.off()
```

### Statistics
```{r}
#BACTERIAL LOAD STATISTICS
S.m_resistance <- lm(log(load_10hr) ~ secondary_dose + primary + rep + secondary_dose:primary, data = S.m_bacterial_load)
S.m_resistance_anova <- anova(S.m_resistance)
S.m_resistance_anova
```

## Figure 2B {.tabset}

### Graph
```{r}
#BACTERIAL LOAD
E.fae_bacterial_load_10hr <- subset(E.fae_bacterial_load, time == 10)

#png(file="E.fae_P.rett_bacterial_load.png",width=1200,height=900,res=130)
ggplot(E.fae_bacterial_load_10hr, aes(x = as.character(secondary_dose), y = log(load), fill = primary)) +
  scale_fill_manual(values=c("gray", "#09b6fc")) +
  geom_boxplot() + 
  theme_classic(base_size = 25) + 
  xlab("secondary dose of P. rettgeri") +
  ylab("log(calculated bacterial load)") +
  geom_point(color = "black", size = 1.1, position=position_jitterdodge())
#dev.off()
```

### Statistics
```{r}
#BACTERIAL LOAD STATISTICS
E.fae_resistance <- lm(log(load) ~ secondary_dose + primary + replicate + secondary_dose:primary, data = E.fae_bacterial_load_10hr)
E.fae_resistance_anova <- anova(E.fae_resistance)
E.fae_resistance_anova
```


## Figure 3A {.tabset}
Chronic infections with S. marcescens provided protection against mortality following highly lethal secondary infection with P. rettgeri 

### Graph
```{r, S.m-P.rett extremes survival data}
#S.m_P.rett_extremes$primary <- relevel(S.m_P.rett_extremes$primary, "PBS")
table(S.m_P.rett_extremes$primary, S.m_P.rett_extremes$secondary_dose)

#THE GRAPH
#png(file="S.m_P.rett_extremes.png",width=1200,height=900,res=130)
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes$day, S.m_P.rett_extremes$status) ~ S.m_P.rett_extremes$primary + S.m_P.rett_extremes$secondary_dose), col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "#003694", "black"), lty=c(3, 3, 3, 3, 3, 3, 1, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 3.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 3.0", "S.m-P.rett 5.0"),col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "#003694", "black"),lty=c(3, 3, 3, 3, 3, 3, 1, 1, 1, 1, 1, 1),lwd=5, cex=1)

#dev.off()
```

### Statistics
```{r}
#STATISTICS
S.m_P.rett_extremes$secondary_dose <- as.factor(S.m_P.rett_extremes$secondary_dose)
S.m_P.rett_extremes_coxph <- coxph(Surv(day, status) ~ secondary_dose + primary + rep + primary:secondary_dose + rep:secondary_dose + rep:primary, data = S.m_P.rett_extremes)
anova(S.m_P.rett_extremes_coxph)
```

### Block 1
```{r, S.m-P.rett extremes survival data 1/30/2020}
S.m_P.rett_extremes_block1 <- subset(S.m_P.rett_extremes, date == "1/30/2020")
table(S.m_P.rett_extremes_block1$primary, S.m_P.rett_extremes_block1$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block1$day, S.m_P.rett_extremes_block1$status) ~ S.m_P.rett_extremes_block1$primary + S.m_P.rett_extremes_block1$secondary_dose), col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "black"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 5.0"),col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 2
```{r, S.m-P.rett extremes survival data 2/13/2020}
S.m_P.rett_extremes_block2 <- subset(S.m_P.rett_extremes, date == "2/13/2020")
table(S.m_P.rett_extremes_block2$primary, S.m_P.rett_extremes_block2$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block2$day, S.m_P.rett_extremes_block2$status) ~ S.m_P.rett_extremes_block2$primary + S.m_P.rett_extremes_block2$secondary_dose), col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "black"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 0.1", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 0.1", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 5.0"),col=c("gray", "#B5E8FC",  "#09B6FC", "#055df5", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 3
```{r, S.m-P.rett extremes survival data 9/27/2020}
S.m_P.rett_extremes_block3 <- subset(S.m_P.rett_extremes, date == "9/27/2020")
table(S.m_P.rett_extremes_block3$primary, S.m_P.rett_extremes_block3$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block3$day, S.m_P.rett_extremes_block3$status) ~ S.m_P.rett_extremes_block3$primary + S.m_P.rett_extremes_block3$secondary_dose), col=c("gray", "#09B6FC", "#055df5", "#003694", "black"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 3.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 3.0", "S.m-P.rett 5.0"),col=c("gray", "#09B6FC", "#055df5", "#003694", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 4
```{r, S.m-P.rett extremes survival data 10/6/2020}
S.m_P.rett_extremes_block4 <- subset(S.m_P.rett_extremes, date == "10/6/2020")
table(S.m_P.rett_extremes_block4$primary, S.m_P.rett_extremes_block4$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block4$day, S.m_P.rett_extremes_block4$status) ~ S.m_P.rett_extremes_block4$primary + S.m_P.rett_extremes_block4$secondary_dose), col=c("gray", "#09B6FC", "#055df5", "#003694", "black"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 3.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 3.0", "S.m-P.rett 5.0"),col=c("gray", "#09B6FC", "#055df5", "#003694", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 5
```{r, S.m-P.rett extremes survival data 11/1/2020}
S.m_P.rett_extremes_block5 <- subset(S.m_P.rett_extremes, date == "11/1/2020")
table(S.m_P.rett_extremes_block5$primary, S.m_P.rett_extremes_block5$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block5$day, S.m_P.rett_extremes_block5$status) ~ S.m_P.rett_extremes_block5$primary + S.m_P.rett_extremes_block5$secondary_dose), col=c("gray", "#09B6FC", "#055df5", "#003694", "black"), lty=c(3, 3, 3, 3, 3, 3, 1, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 3.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 3.0", "S.m-P.rett 5.0"),col=c("gray", "#09B6FC", "#055df5", "#003694", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 6
```{r, S.m-P.rett extremes survival data 6/16/2021}
S.m_P.rett_extremes_block6 <- subset(S.m_P.rett_extremes, date == "6/16/2021")
table(S.m_P.rett_extremes_block6$primary, S.m_P.rett_extremes_block6$secondary_dose)

#THE GRAPH
par(mar=c(4,5,1,1))
plot(survfit(Surv(S.m_P.rett_extremes_block6$day, S.m_P.rett_extremes_block6$status) ~ S.m_P.rett_extremes_block6$primary + S.m_P.rett_extremes_block6$secondary_dose), col=c("gray", "#09B6FC", "#055df5", "#003694", "black"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=5, yaxt='n', xaxt='n', ylab="proportion alive", xlab="days post-secondary infection", cex.lab=2.5, xlim=c(0,7), xaxs='i') 
axis(2, las=2, cex.axis=1.5, lwd=5)
axis(1, cex.axis=1.5, lwd=5)
box(lwd=5)

#THE LEGEND
legend("topright",inset=0, bty="n" , c("PBS-PBS", "PBS-P.rett 1.0", "PBS-P.rett 2.0", "PBS-P.rett 3.0", "PBS-P.rett 5.0", "S.m-PBS", "S.m-P.rett 1.0", "S.m-P.rett 2.0", "S.m-P.rett 3.0", "S.m-P.rett 5.0"),col=c("gray", "#09B6FC", "#055df5", "#003694", "black"),lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=5, cex=1)
```


## Figure 3B {.tabset}
Things

### Graph
Mortality following secondary infection with P. rettgeri in flies chronically infected with S. marcescens versus control flies not given a chronic infection. Flies chronically infected with S. marcescens were more likely to survive various doses of secondary infection with P. sneebia (p < 0.0001).
```{r, S.m-P.snee survival data}
#table(S.m_P.snee$primary, S.m_P.snee$secondary_dose)

#png(file="S.m_P.snee.png",  width = 1700, height = 1500, res = 300)
#par(mar=c(4,4,0.1,0.1)) #sets the margins around the graph so there is room for the labels
plot(survfit(Surv(S.m_P.snee$hour, S.m_P.snee$status) ~ S.m_P.snee$primary + S.m_P.snee$secondary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=2.3, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i') 
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-PBS", "0.001", "PBS-0.01", "PBS-0.1", "PBS-1.0", "S.m-PBS", "S.m-0.001", "S.m-0.01", "S.m-0.1", "S.m-1.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=4, cex=1)

#STATISTICS
S.m_P.snee$secondary_dose <- as.factor(S.m_P.snee$secondary_dose)
S.m_P.snee_coxph <- coxph(Surv(day, status) ~ secondary_dose + primary + rep + primary:secondary_dose + rep:secondary_dose + rep:primary, data = S.m_P.snee)
#summary(S.m_P.snee_coxph)
anova(S.m_P.snee_coxph)
```

### Block 1
```{r, S.m-P.snee 10/1/2020}
S.m_P.snee_block1 <- subset(S.m_P.snee, date == "10/1/2020")
table(S.m_P.snee_block1$primary, S.m_P.snee_block1$secondary_dose)


plot(survfit(Surv(S.m_P.snee_block1$hour, S.m_P.snee_block1$status) ~ S.m_P.snee_block1$primary + S.m_P.snee_block1$secondary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=2.3, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i') 
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-PBS", "0.001", "PBS-0.01", "PBS-0.1", "PBS-1.0", "S.m-PBS", "S.m-0.001", "S.m-0.01", "S.m-0.1", "S.m-1.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=4, cex=1)
```

### Block 2
```{r, S.m-P.snee 10/10/2020}
S.m_P.snee_block2 <- subset(S.m_P.snee, date == "10/10/2020")
table(S.m_P.snee_block2$primary, S.m_P.snee_block2$secondary_dose)


plot(survfit(Surv(S.m_P.snee_block2$hour, S.m_P.snee_block2$status) ~ S.m_P.snee_block2$primary + S.m_P.snee_block2$secondary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=2.3, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i') 
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-PBS", "0.001", "PBS-0.01", "PBS-0.1", "PBS-1.0", "S.m-PBS", "S.m-0.001", "S.m-0.01", "S.m-0.1", "S.m-1.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=4, cex=1)
```

### Block 3
```{r, S.m-P.snee 10/24/2020}
S.m_P.snee_block3 <- subset(S.m_P.snee, date == "10/24/2020")
table(S.m_P.snee_block3$primary, S.m_P.snee_block3$secondary_dose)

plot(survfit(Surv(S.m_P.snee_block3$hour, S.m_P.snee_block3$status) ~ S.m_P.snee_block3$primary + S.m_P.snee_block3$secondary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1), lwd=2.3, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i') 
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-PBS", "0.001", "PBS-0.01", "PBS-0.1", "PBS-1.0", "S.m-PBS", "S.m-0.001", "S.m-0.01", "S.m-0.1", "S.m-1.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5"), lty=c(3, 3, 3, 3, 3, 1, 1, 1, 1, 1),lwd=4, cex=1)
```


## Figure 4A {.tabset}
Text here 

### Graph
```{r, S.m-P.rett varied primary survival data}
P.rett_varied_primary = subset(P.rett_varied_primary, secondary == "P.rett")
P.rett_varied_primary$primary_dose <- as.factor(P.rett_varied_primary$primary_dose)

#png(file="P.rett_varied_primary_no_legend.png",  width = 1700, height = 1500, res = 300)
par(mar=c(4,4,0.1,0.1)) #sets the margins around the graph so there is room for the labels
plot(survfit(Surv(P.rett_varied_primary$day, P.rett_varied_primary$status) ~ P.rett_varied_primary$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)


#STATISTICS
#Generate a Cox proportional Hazards model which assesses the contribution of infectious dose while controlling for replicate
P.rett_varied_primary_coxph <- coxph(Surv(day, status) ~ primary_dose, data = P.rett_varied_primary)
#summary(P.rett_varied_primary_coxph)
anova(P.rett_varied_primary_coxph)
```

### Block 1
```{r, S.m-P.rett varied primary 10/18/2020}
P.rett_varied_primary_block1 <- subset(P.rett_varied_primary, date == "10/18/2020")
table(P.rett_varied_primary_block1$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block1$day, P.rett_varied_primary_block1$status) ~ P.rett_varied_primary_block1$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 2
```{r, S.m-P.rett varied primary 10/20/2020}
P.rett_varied_primary_block2 <- subset(P.rett_varied_primary, date == "10/20/2020")
table(P.rett_varied_primary_block2$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block2$day, P.rett_varied_primary_block2$status) ~ P.rett_varied_primary_block2$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 3
```{r, S.m-P.rett varied primary 10/29/2020}
P.rett_varied_primary_block3 <- subset(P.rett_varied_primary, date == "10/29/2020")
table(P.rett_varied_primary_block3$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block3$day, P.rett_varied_primary_block3$status) ~ P.rett_varied_primary_block3$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 4
```{r, S.m-P.rett varied primary 11/2/2020}
P.rett_varied_primary_block4 <- subset(P.rett_varied_primary, date == "11/2/2020")
table(P.rett_varied_primary_block4$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block4$day, P.rett_varied_primary_block4$status) ~ P.rett_varied_primary_block4$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 5
```{r, S.m-P.rett varied primary 11/7/2020}
P.rett_varied_primary_block5 <- subset(P.rett_varied_primary, date == "11/7/2020")
table(P.rett_varied_primary_block5$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block5$day, P.rett_varied_primary_block5$status) ~ P.rett_varied_primary_block5$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 6
```{r, S.m-P.rett varied primary 11/28/2020}
P.rett_varied_primary_block6 <- subset(P.rett_varied_primary, date == "11/28/2020")
table(P.rett_varied_primary_block6$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block6$day, P.rett_varied_primary_block6$status) ~ P.rett_varied_primary_block6$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 7
```{r, S.m-P.rett varied primary 11/30/2020}
P.rett_varied_primary_block7 <- subset(P.rett_varied_primary, date == "11/30/2020")
table(P.rett_varied_primary_block7$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block7$day, P.rett_varied_primary_block7$status) ~ P.rett_varied_primary_block7$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 8
```{r, S.m-P.rett varied primary 12/4/2020}
P.rett_varied_primary_block8 <- subset(P.rett_varied_primary, date == "12/4/2020")
table(P.rett_varied_primary_block8$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block8$day, P.rett_varied_primary_block8$status) ~ P.rett_varied_primary_block8$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 9
```{r, S.m-P.rett varied primary 6/17/2021}
P.rett_varied_primary_block9 <- subset(P.rett_varied_primary, date == "6/17/2021")
table(P.rett_varied_primary_block9$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block9$day, P.rett_varied_primary_block9$status) ~ P.rett_varied_primary_block9$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 10
```{r, S.m-P.rett varied primary 6/18/2021}
P.rett_varied_primary_block10 <- subset(P.rett_varied_primary, date == "6/18/2021")
table(P.rett_varied_primary_block10$primary_dose)

par(mar=c(4,4,0.1,0.1))
plot(survfit(Surv(P.rett_varied_primary_block10$day, P.rett_varied_primary_block10$status) ~ P.rett_varied_primary_block10$primary_dose), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Days Post-Secondary Infection", cex.lab=1.3, xlim=c(0,7), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.rett 2.0", "S.m 0.001-P.rett 2.0", "S.m 0.01-P.rett 2.0", "S.m 0.1-P.rett 2.0", "S.m 1.0-P.rett 2.0", "S.m 2.0-P.rett 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

## Figure 4B {.tabset}
words

### Graph
```{r, S.m-P.snee varied primary survival data}
P.snee_varied_primary <- subset(P.snee_varied_primary, secondary == "P.snee")
table(P.snee_varied_primary$date, P.snee_varied_primary$primary_dose)

#png(file="P.snee_varied_primary.png",  width = 1700, height = 1500, res = 300)
#par(mar=c(4,4,0.1,0.1)) #sets the margins around the graph so there is room for the labels
plot(survfit(Surv(P.snee_varied_primary$hour, P.snee_varied_primary$status) ~ P.snee_varied_primary$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)

#STATISTICS
#Generate a Cox proportional Hazards model which assesses the contribution of primary dose while controlling for replicate
#table(P.snee_varied_primary$primary, P.snee_varied_primary$primary_dose)
P.snee_varied_primary$primary <- as.factor(P.snee_varied_primary$primary)
P.snee_varied_primary$primary_dose <- as.factor(P.snee_varied_primary$primary_dose)
P.snee_varied_primary_coxph <- coxph(Surv(hour, status) ~ primary_dose, data = P.snee_varied_primary)
#summary(P.snee_varied_primary_coxph)
anova(P.snee_varied_primary_coxph)
```

### Block 1
```{r, P.snee varied primary 3/10/2021}
P.snee_varied_primary_block1 <- subset(P.snee_varied_primary, date == "3/10/2021")
table(P.snee_varied_primary$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block1$hour, P.snee_varied_primary_block1$status) ~ P.snee_varied_primary_block1$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 2
```{r, P.snee varied primary 3/17/2021}
P.snee_varied_primary_block2 <- subset(P.snee_varied_primary, date == "3/17/2021")
table(P.snee_varied_primary_block2$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block2$hour, P.snee_varied_primary_block2$status) ~ P.snee_varied_primary_block2$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 3
```{r, P.snee varied primary 3/31/2021}
P.snee_varied_primary_block3 <- subset(P.snee_varied_primary, date == "3/31/2021")
table(P.snee_varied_primary_block3$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block3$hour, P.snee_varied_primary_block3$status) ~ P.snee_varied_primary_block3$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 4
```{r, P.snee varied primary 4/21/2021}
P.snee_varied_primary_block4 <- subset(P.snee_varied_primary, date == "4/21/2021")
table(P.snee_varied_primary_block4$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block4$hour, P.snee_varied_primary_block4$status) ~ P.snee_varied_primary_block4$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 5
```{r, P.snee varied primary 4/28/2021}
P.snee_varied_primary_block4 <- subset(P.snee_varied_primary, date == "4/28/2021")
table(P.snee_varied_primary_block4$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block4$hour, P.snee_varied_primary_block4$status) ~ P.snee_varied_primary_block4$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```

### Block 6
```{r, P.snee varied primary 6/20/2021}
P.snee_varied_primary_block6 <- subset(P.snee_varied_primary, date == "6/20/2021")
table(P.snee_varied_primary_block6$primary_dose)

plot(survfit(Surv(P.snee_varied_primary_block6$hour, P.snee_varied_primary_block6$status) ~ P.snee_varied_primary_block6$condition), col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"), lty=c(1, 1, 1, 1, 1, 1), lwd=3.4, yaxt='n', xaxt='n', ylab="Proportion Alive", xlab="Hours Post-Secondary Infection", cex.lab=1.3, xlim=c(10,48), xaxs='i', ylim=c(0, 1.05), yaxs='i')  
axis(2, las=2, cex.axis=1, lwd=4.5) 
axis(1, cex.axis=1, lwd=4.5)
box(lwd=4.5)

legend("bottomleft", bty="n" , c("PBS-P.snee 2.0", "S.m 0.001-P.snee 2.0", "S.m 0.01-P.snee 2.0", "S.m 0.1-P.snee 2.0", "S.m 1.0-P.snee 2.0", "S.m 2.0-P.snee 2.0"),col=c("gray", "#B5E8FC", "#75D6FD", "#09B6FC", "#055df5", "#003694"),lty=c(1, 1, 1, 1, 1, 1),lwd=5, cex=1)
```
