---
title: "Logistic_models"
author: "Madyline Lawrence"
date: "7/14/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
# Importing packages needed

library(gdata)
library(ggplot2)
library(stringr)
library(boot)
library(data.table)
library(dplyr)
library(formattable)
library(tidyr)
library(caret)
library(questionr)
library(DescTools)
library(survival)
```

**Cleaning of data**

```{r}
rm(list=ls()) #removes all old variables
E.fae_data_with2 = read.csv("E.fae resistance data.csv")
E.fae_data = subset(E.fae_data_with2, dose != 2)
S.m_data = read.csv("S.m resistance data.csv")

```


```{r, echo = FALSE}
#import the dataset

efdata = read.xls("ef_Complete Survival Data.xlsx")
smdata = read.xls("sm_Complete Survival Data.xlsx")

```

```{r, echo = FALSE}
#turns white spaces into nothing

efdata = trim(efdata)
smdata = trim(smdata) 
```

```{r, echo = FALSE}
#changes all blank values to NA and exclude bad rows

efdata[efdata==""] <- NA
smdata[smdata==""] <- NA

#ffdata[ffdata== "None" |ffdata== "Unknown" | ffdata == "Not Applicable"] <- NA

efdata = efdata[,c(2,3,4,6,7,8,9,10,11,12,13)]
smdata = smdata[,c(2,3,4,6,7,8,9,10,11,12,13)]
```



```{r, echo = FALSE}
# remove rows without values for 0 and 10 hours

efdata = efdata[!is.na(efdata$X0.hour),]
efdata = efdata[!is.na(efdata$X10.hour),]

smdata = smdata[!is.na(smdata$X0.hour),]
smdata = smdata[!is.na(smdata$X10.hour),]
```

```{r, echo = FALSE}
efdata$bin_primary = ifelse(efdata$primary == "E.fae", 1, 0)
efdata$bin_alive3 = ifelse(efdata$alive3 == TRUE, 1, 0)

smdata$bin_primary = ifelse(smdata$primary == "S.M", 1, 0)
smdata$bin_alive3 = ifelse(smdata$alive3 == TRUE, 1, 0)
```


```{r, echo = FALSE}

ef.bygroup = distinct(efdata, scientist,rep, primary, X2_dose, X0.hour, X10.hour, log10_10hour)


sm.bygroup = distinct(smdata, scientist, rep, primary, X2_dose, X0.hour, X10.hour, log10_10hour)
```



#E.Fae Data:

##Logistic Graph by chronic infection status Significance:



```{r, echo = FALSE}

PBS = efdata[efdata$primary == "PBS",]

PBSlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = PBS)

summary(PBSlogit)

PseudoR2(PBSlogit)

Cstat(PBSlogit)

bact_val = seq(2,9,0.01)

PBS_preds <- predict(PBSlogit, list(log10_10hour = bact_val), type = "response", se.fit = TRUE)




Efae = efdata[efdata$primary == "E.fae",]

Efaelogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = Efae)

summary(Efaelogit)

Cstat(Efaelogit)

Efae_preds <- predict(Efaelogit, list(log10_10hour = bact_val), type = "response")


```


##Values of Interest

PBS curve point of inflection = 3.6822

PBS hill slope = -0.15480

E.fae curve point of inflection = 4.56533

E.fae hill slope = -0.13400



## Logistic Model Including Interaction Significance
```{r, echo = FALSE}


mylogit = glm(formula = bin_alive3 ~ log10_10hour + bin_primary + (bin_primary*log10_10hour), family = "binomial", data = efdata)

summary(mylogit)

Cstat(mylogit)

```

E.FAE IMAGES:



```{r, echo = FALSE}
PBS = efdata[efdata$primary == "PBS",]

PBSlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = PBS)

summary(PBSlogit)

PseudoR2(PBSlogit)

Cstat(PBSlogit)

bact_val = seq(2,9,0.01)

PBS_preds <- predict(PBSlogit, list(log10_10hour = bact_val), type = "response",se.fit =TRUE)

PBS_upper = (PBS_preds$fit+1.96*PBS_preds$se.fit)
PBS_lower = (PBS_preds$fit-1.96*PBS_preds$se.fit)

Efae = efdata[efdata$primary == "E.fae",]

Efaelogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = Efae)



summary(Efaelogit)

Cstat(Efaelogit)

Efae_preds <- predict(Efaelogit, list(log10_10hour = bact_val), type = "response",se.fit = TRUE)

Efae_upper = (Efae_preds$fit+(1.96*Efae_preds$se.fit))
Efae_lower = (Efae_preds$fit-(1.96*Efae_preds$se.fit))







png(file="figure6_abbyfrank.png", width = 1500, height = 1500, res = 300)
par(family = "Times")

plot(0,0,xlim = c(2,9),ylim = c(0,1),type = "n",ylab= "Probability of Survival", xlab = expression("Log"[10]*"(10 Hour Bacterial Load)"))

lines(PBS_preds$fit~bact_val,col="steelblue4", lwd = 2)

lines(Efae_preds$fit~bact_val, col="steelblue2", lwd = 2)

legend("topright", inset=.03, title="Primary Infection Group",c("PBS","E.faecalis"), fill=c("steelblue4","steelblue2"), horiz=TRUE,cex = 0.75)
 
lines(bact_val, PBS_upper, lty=2, col="steelblue4")
lines(bact_val, PBS_lower, lty=2,col="steelblue4")

lines(bact_val, Efae_upper, lty=2, col="steelblue2")
lines(bact_val, Efae_lower, lty=2, col="steelblue2")

dev.off()



```





#SM DATA:

##Logistic Graph by chronic infection status:

```{r, echo = FALSE}

PBS = smdata[smdata$primary == "PBS",]

PBSlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = PBS)

summary(PBSlogit)

PseudoR2(PBSlogit)

Cstat(PBSlogit)

bact_val = seq(2,9,0.01)


PBS_preds <- predict(PBSlogit, list(log10_10hour = bact_val), type = "response")




SM = smdata[smdata$primary == "S.M",]

SMlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = SM)

summary(SMlogit)


Cstat(SMlogit)

SM_preds <- predict(SMlogit, list(log10_10hour = bact_val), type = "response")

ggplot() + geom_line(aes(x = bact_val, y = PBS_preds, colour = "PBS")) + geom_line(aes(x = bact_val, y = SM_preds, colour = "SM")) + ylab("Probability of Survival") + xlab("Log (10 Hour Bacteria Amount)") 


```


##Values of Interest

PBS curve point of inflection = 3.6981

PBS hill slope = -0.26585

S.M curve point of inflection = 5.71890

S.M hill slope = -0.10105

## Logistic Model Including Interaction Significance
```{r, echo = FALSE}


mylogit = glm(formula = bin_alive3 ~ log10_10hour + bin_primary + (bin_primary*log10_10hour), family = "binomial", data = smdata)

summary(mylogit)

Cstat(mylogit)

```



SM IMAGES:

```{r, echo = FALSE}
PBS = smdata[smdata$primary == "PBS",]

PBSlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = PBS)

summary(PBSlogit)

PseudoR2(PBSlogit)

Cstat(PBSlogit)

bact_val = seq(2,9,0.01)


PBS_preds <- predict(PBSlogit, list(log10_10hour = bact_val), type = "response", se.fit = TRUE)

PBS_upper = (PBS_preds$fit+(1.96*PBS_preds$se.fit))
PBS_lower = (PBS_preds$fit-(1.96*PBS_preds$se.fit))


SM = smdata[smdata$primary == "S.M",]

SMlogit = glm(formula = alive3 ~ log10_10hour, family = "binomial", data = SM)

summary(SMlogit)


Cstat(SMlogit)

SM_preds <- predict(SMlogit, list(log10_10hour = bact_val), type = "response", se.fit = TRUE)

SM_upper = (SM_preds$fit+(1.96*SM_preds$se.fit))
SM_lower = (SM_preds$fit-(1.96*SM_preds$se.fit))


png(file="figure13_abbyfrank.png", width = 1500, height = 1500, res = 300)
par(family = "Times")



plot(0,0,xlim = c(2,9),ylim = c(0,0.9),type = "n",ylab= "Probability of Survival", xlab = expression("Log"[10]*"(10 Hour Bacterial Load)"))

lines(PBS_preds$fit~bact_val,col="steelblue4", lwd = 2)

lines(SM_preds$fit~bact_val, col="steelblue2", lwd = 2)

legend("topright", inset=.03, title="Primary Infection Group",c("PBS","S.marcescens"), fill=c("steelblue4","steelblue2"), horiz=TRUE,cex = 0.75)
 
lines(bact_val, PBS_upper, lty=2, col="steelblue4")
lines(bact_val, PBS_lower, lty=2, col="steelblue4")

lines(bact_val, SM_upper, lty=2, col="steelblue2")
lines(bact_val, SM_lower, lty=2, col="steelblue2")


dev.off()


```

```{r}
# Significance of control vs efae

mylogit = glm(formula = alive3 ~ log10_10hour + primary, family = "binomial", data = efdata)

summary(mylogit)


# Significance of control vs sm

mylogit = glm(formula = alive3 ~ log10_10hour + primary, family = "binomial", data = smdata)

summary(mylogit)
```


